FoRTE baseline

### 2019-04-24 analysis/paper/paper.Rmd
Remove CV from sensitivity plot, and tweak paper

- Which parameters contribute the most uncertainty?
- Structural vs. parameteric uncertainty

Different model configurations produce significantly different ecological trajectories.

```{r uncertainty-analysis, fig.cap = uncertainty_analysis_cap, fig.dim = c(20, 15)}
uncertainty_analysis_cap <- paste(
  "PEcAn-liked parameter sensitivity and uncertainty analysis, by model type."
)
readd(sensitivity_plot)
```

@@

>>>>

```{r uncertainty-analysis, fig.cap = uncertainty_analysis_cap, fig.dim = c(15, 15)}
uncertainty_analysis_cap <- paste(
  "PEcAn-liked parameter sensitivity and uncertainty analysis, by model type.",
  "Elasticity (a) is the normalized sensitivity of the model to a fixed change in the parameter.",
  "pvar (b) is the partial variance, which describes the overall contribution of the parameter to model predictive uncertainty based on the combination of parameter uncertainty and model sensitivity.",
  "Input parameter distributions are shown in Figure XXX."
)
readd(sensitivity_plot)
```

@@

Take-away: Model parameter uncertainty is sensitive to model configuration.
For example, turning on the finite canopy radius with the two-stream canopy RTM increases sensitivity across many parameters.

**TODO**: Structural vs. parameteric uncertainty
